A Comparison of Graph Processing Systems

### 2020-09-23 documentation/paper/sections/results/sssp.tex

\begin{table}
\renewcommand{\arraystretch}{1.1}
\tiny
\centering
\caption{Distributed SSSP Execution Times and Their Realation to Galois Push}
\begin{tabular}{c@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r}
\toprule
\bf{Data Set}&
\multicolumn{2}{c}{\bf Galois Push}&\multicolumn{2}{c}{\bf Galois Pull}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
\cmidrule{2-3}\cmidrule{4-5}\cmidrule{6-7}\cmidrule{8-9}
&$\times$G.Push&time (s)&$\times$G.Push&time (s)&$\times$G.Push&time (s)&$\times$G.Push&time (s)\\\midrule
flickr & 1.0 & 2.4 & 0.97 & 2.4 & 1.02 & 2.5 & 17.46 & 42.6\\
orkut & 1.0 & 4.2 & 1.28 & 5.4 & 4.12 & 17.3 & 14.38 & 60.4\\
wikipedia & 1.0 & 14.2 & 1.88 & 26.6 & 5.26 & 74.5 & 7.11 & 100.8 \\
twitter & 1.0 & 40.0 & 3.56 & 142.2 & 9.79 & 391.1 & 8.76 & 349.9\\
rMat27 & 1.0 & 39.0 & 3.98 & 154.9 & 9.91 & 386.0 & 14.52 & 565.8\\
friendster & 1.0 & 58.5 & 2.32 & 136.0 & 9.72 & 568.9 & 7.59 & 444.0\\
rMat28 & 1.0 & 71.5 & 5.7 & 407.9 & 11.07 & 792.0 & 16.5 & 1180.2\\\bottomrule
\end{tabular}
\label{tbl:ssspexec}
\end{table}

>>>>

\begin{table*}
\renewcommand{\arraystretch}{1.2}
\renewcommand{\rot}[1]{\rotatebox{90}{#1}}
\centering
\caption{Distributed SSSP Execution Times and Their Realation to Galois Push}
\begin{tabular}{c@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r@{\tabskip 1.4 \tabcolsep}r@{\tabskip 1 \tabcolsep}r}
\toprule
&
\multicolumn{2}{c}{\bf Galois Push}&\multicolumn{2}{c}{\bf Galois Pull}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
\cmidrule{2-3}\cmidrule{4-5}\cmidrule{6-7}\cmidrule{8-9}
\bf{Data Set}&$\times$G.Push&time (s)&$\times$G.Push&time (s)&$\times$G.Push&time (s)&$\times$G.Push&time (s)\\\midrule
flickr & 1.0 & 2.4 & 0.97 & 2.4 & 1.02 & 2.5 & 17.46 & 42.6\\
orkut & 1.0 & 4.2 & 1.28 & 5.4 & 4.12 & 17.3 & 14.38 & 60.4\\
wikipedia & 1.0 & 14.2 & 1.88 & 26.6 & 5.26 & 74.5 & 7.11 & 100.8 \\
twitter & 1.0 & 40.0 & 3.56 & 142.2 & 9.79 & 391.1 & 8.76 & 349.9\\
rMat27 & 1.0 & 39.0 & 3.98 & 154.9 & 9.91 & 386.0 & 14.52 & 565.8\\
friendster & 1.0 & 58.5 & 2.32 & 136.0 & 9.72 & 568.9 & 7.59 & 444.0\\
rMat28 & 1.0 & 71.5 & 5.7 & 407.9 & 11.07 & 792.0 & 16.5 & 1180.2\\\bottomrule
\end{tabular}
\label{tbl:ssspexec}
\end{table*}
